Tools for identifying implausible counts

### 2019-04-06 Rmd/count_check_MS.Rmd
yaml

---
title: "Tools for identifying implausible counts"
author: |
  | Richard J. Telford 
  | Department of Biological Sciences, University of Bergen, Postboks 7803, N-5020 Bergen, Norway
  | email: richard.telford@uib.no
date: "`r format(Sys.Date(), '%d %B %Y')`"
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{pdflscape}
   - \newcommand{\blandscape}{\begin{landscape}}
   - \newcommand{\elandscape}{\end{landscape}}   
output:
  bookdown::pdf_document2:
      latex_engine: xelatex
      number_sections: true
documentclass: article
classoption: a4paper
bibliography: extra/countMS2.bib
csl: extra/journal-of-paleolimnology.csl
toc: false
---

@@

# Abstract{-}

@@

Data sets were downloaded from the Palaeodata Center, Neotoma, Pangaea and other sources. A range of ecological and palaeoecological data were sought to allow for difference in typical count sum and species richness. This paper does not attempt to be an exhaustive survey of all the data available.

@@

Dataset 3 is a `r n_groups(readd(pollen1_counts))` count pollen stratigraphy extracted from Neotoma. The associated paper (anonymised here) reports that count sums are 200 (excluding fern spores). Unexpectedly, only `r pollen1_summary$count$has_singletons %>% insist(. == 1) %>% as.english()` of the counts has a singleton. The other counts have minimum abundances of two or four pollen grains. With the exception of the single singleton, all `r pollen1_summary$individual$n %>% invisible()` species counts are divisible by two`r pollen1_summary$individual$not_two %>% insist(. == 1) %>% invisible()`. The probablility that these counts reflects the true nature of the pollen assemblages is exceedingly low; it is far more likely that the data have been mishandled in some way.

>>>>

---
title: "Tools for identifying implausible counts"
author:
  - name: Richard J. Telford
    email: richard.telford@uib.no
    affiliation: University of Bergen
    footnote: Corresponding Author
address:
  - code: University of Bergen
    address: Department of Biological Sciences, University of Bergen and Bjerknes Centre for Climate Research, Postboks 7803, N-5020 Bergen, Norway
abstract: |
  Astract goes here
journal: "Quaternary Science Reviews"
date: "`r format(Sys.Date(), '%d %B %Y')`"
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{pdflscape}
   - \newcommand{\blandscape}{\begin{landscape}}
   - \newcommand{\elandscape}{\end{landscape}}   
output:
  bookdown::pdf_book:
    base_format: 
      rticles::elsevier_article
    number_sections: true
documentclass: article
classoption: a4paper
bibliography: extra/countMS2.bib
csl: extra/journal-of-paleolimnology.csl
---

@@

@@

Data sets were downloaded from the Palaeodata Center, Neotoma, Pangaea and other sources. A range of ecological and palaeoecological data were sought to allow for difference in typical count sum and species richness. Datasets with possible data mishandling are anonymised. This paper does not attempt to be an exhaustive survey of all the data available.

@@

Dataset 3 is a `r n_groups(readd(pollen1_counts))` count pollen stratigraphy. The associated paper reports that count sums are 200 (excluding fern spores). Unexpectedly, only `r pollen1_summary$count$has_singletons %>% insist(. == 1) %>% as.english()` of the counts has a singleton. The other counts have minimum abundances of two or four pollen grains. With the exception of the single singleton, all `r pollen1_summary$individual$n %>% invisible()` species counts are divisible by two`r pollen1_summary$individual$not_two %>% insist(. == 1) %>% invisible()`. The probablility that these counts reflects the true nature of the pollen assemblages is exceedingly low; it is far more likely that the data have been mishandled in some way.
